PANCHANGE_data_preprocessing

### 2020-08-19 PANCHANGE_data_preprocessing2020-07-15.Rmd
changed diff score naming

# Gender categories synchronised

```{r gender recoding for GLAD}
if(GLAD == TRUE | NBR == TRUE) {

@@

# Difference score for prepandemic and baseline phq sum scores
dat <- dat %>%
  mutate(
    phq.diff_score_prepan_base =
      as.numeric(
        phq.sum_score_base - phq.sum_score_prepan  # baseline sum score MINUS prepandemic sum score 
      )
  )

@@

# Difference score for prepandemic and baseline gad sum scores
dat <- dat %>%
  mutate(
    gad.diff_score_prepan_base =
      as.numeric(
        gad.sum_score_base - gad.sum_score_prepan  # baseline sum score MINUS prepandemic sum score 
      )
  )

@@

PCL difference scores
NOTE: Only computed baseline and prepandemic differences as the retro account here isn't actually retrospective, but whether the reported baseline scores are due to the pandemic. 
```{r pcl difference scores}
if(GLAD == TRUE | EDGI == TRUE){
# Difference score for prepandemic and baseline pcl sum scores
dat <- dat %>%
  mutate(
    pcl.diff_score_prepan_base =
      as.numeric(
        pcl.sum_score_base - pcl.sum_score_prepan  # baseline sum score MINUS prepandemic sum score 
      )
  )

@@

>>>>

# Gender categories synchronised
RAMP has the correct Gender categories so does not need editing. 
```{r gender recoding for GLAD}
if(GLAD == TRUE | NBR == TRUE) {

@@

# Difference score for prepandemic and baseline phq sum scores
dat <- dat %>%
  mutate(
    phq.diff_score_base_prepan =
      as.numeric(
        phq.sum_score_base - phq.sum_score_prepan  # baseline sum score MINUS prepandemic sum score 
      )
  )

@@

# Difference score for prepandemic and baseline gad sum scores
dat <- dat %>%
  mutate(
    gad.diff_score_base_prepan =
      as.numeric(
        gad.sum_score_base - gad.sum_score_prepan  # baseline sum score MINUS prepandemic sum score 
      )
  )

@@

PCL difference scores
NOTE: Only computed baseline and prepandemic differences as the retro account here isn't actually retrospective, but whether the reported baseline scores are due to the pandemic. 
```{r pcl difference scores}
if(GLAD == TRUE | EDGI == TRUE){
# Difference score for prepandemic and baseline pcl sum scores
dat <- dat %>%
  mutate(
    pcl.diff_score_base_prepan =
      as.numeric(
        pcl.sum_score_base - pcl.sum_score_prepan  # baseline sum score MINUS prepandemic sum score 
      )
  )

@@

# Rename NBR Sample ID 
```{r rename NBR sample ID}
if(NBR == TRUE){
dat.coping <- dat.coping %>%
  recode(Sample,
         "SP0068" = "NBR"
         )
}
```
